Estimation of Fractional-N PLL Linearity Limits and Cycle Slipping

### 2025-06-04 CaseStudies/Example3_4_SimulationandEstimationofLoopSettlingTimes/article/article.qmd
Finishing 3.4th example.

@@

| **Symbol**       | **Description**  | **Value**                                       |
|------------------|------------------|-------------------------------------------------|
| $C_1$            | Series capacitor | `{python} format(C_1)`F                         |
| $R_1$            | Series resistor  | `{python} format(R_1)`$\Omega$                  |
| $C_2$            | Shunt capacitor  | `{python} format(C_2)`F                         |
| $f_\mathrm{VCO}$ | VCO freq.        | `{python} format(fvco)`Hz                       |
| $K_\mathrm{VCO}$ | VCO sensivity    | `{python} format(Kvco)`Hz/V                     |
| $\theta_{e_m}$   | Max. Phase Error | `{python} format_with_pi_latex(theta_e_m)`rad   |
| $I_\mathrm{CP}$  | CP Current       | `{python} format(I_CP)`A                        |
| $A_0$            | DC Gain          | `{python} format(A0)`                           |
| $f_\mathrm{bw}$  | Bandwidth        | `{python} format(f_bw)`Hz                       |
| $f_r$            | Ref. freq.       | `{python} format(f_r)`Hz                        |
| $N$              | Divider          | `{python} format(N)`                           |
| $\Delta f_m$     | Max. Step freq.  | `{python} format(step_m_lin)`Hz                 |
| $t_s$            | Settling time    | `{python} format(t_s)`s                         |

>>>>

T_s = 2 * np.pi * 3e6 / (np.pi * omega_n_meas**2)
```

@@

| **Symbol**       | **Description**        | **Value**                                       |
|------------------|------------------------|-------------------------------------------------|
| $C_1$            | Series capacitor       | `{python} format(C_1)`F                         |
| $R_1$            | Series resistor        | `{python} format(R_1)`$\Omega$                  |
| $C_2$            | Shunt capacitor        | `{python} format(C_2)`F                         |
| $f_\mathrm{VCO}$ | VCO freq.              | `{python} format(fvco)`Hz                       |
| $K_\mathrm{VCO}$ | VCO sensivity          | `{python} format(Kvco)`Hz/V                     |
| $\theta_{e_m}$   | Max. Phase Error       | `{python} format_with_pi_latex(theta_e_m)`rad   |
| $I_\mathrm{CP}$  | CP Current             | `{python} format(I_CP)`A                        |
| $A_0$            | DC Gain                | `{python} format(A0)`                           |
| $f_\mathrm{bw}$  | Bandwidth              | `{python} format(f_bw)`Hz                       |
| $f_r$            | Ref. freq.             | `{python} format(f_r)`Hz                        |
| $N$              | Divider                | `{python} format(N)`                           |
| $\Delta f_m$     | Max. Step freq.        | `{python} format(step_m_lin)`Hz                 |
| $t_s$            | Settling time          | `{python} format(t_s)`s                         |
| $T_s$            | 3 MHz Acquisition time | `{python} format(T_s)`s                         |
